---
title: 'SEEDY Exploration'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(seedy)
library(dplyr)
```

## Simulation Parameters (SIR with Admissions & Discharges)
| Parameter | Default Value | Description |
| :--- | :--- | :--- |
| **beta** | `0.002` | **Infection rate:** Probability of transmission per $S$-$I$ contact. |
| **gamma** | `0.001` | **Recovery rate:** Rate at which infected individuals recover ($1/duration$). |
| **delta** | `0.001` | **Turnover rate:** Rate of population replacement (births/deaths). |
| **N** | `50` | **Population size:** Total number of individuals in the simulation. |
| **tmax** | `5000` | **Time horizon:** The maximum duration of the simulation. |
| **seed** | `1` | **Random seed:** Ensures the simulation results are reproducible. |
---


## Output Format

| Column Name | Type | Description |
| :--- | :--- | :--- |
| **inf.ID** | `integer` | Unique ID of the infected individual. |
| **inf.times** | `numeric` | Time ($t$) at which the individual was infected. |
| **rec.times** | `numeric` | Time ($t$) at which the individual recovered or was removed. |
| **inf.source** | `integer` | The ID of the person who infected them (0 = index case). |

#### SIR (not SEEDY)
```{r}
simulate_SIR <- function(
  beta = 0.002,
  gamma = 0.001,
  delta = 0.001,
  tmax = 5000,
  N = 50,
  seed = 1
) {
  set.seed(seed)
  
  t <- 0
  next_id <- 1
  
  S <- list()
  I <- list()
  all_people <- list()
  
  # --- Initialize population ---
  for (i in 1:N) {
    person <- list(id = next_id, inf_time = NULL, rec_time = NULL, source = NULL)
    S[[length(S)+1]] <- person
    all_people[[as.character(next_id)]] <- person
    next_id <- next_id + 1
  }
  
  # --- Seed infection ---
  idx <- sample(seq_along(S), 1)
  person <- S[[idx]]
  S <- S[-idx]
  
  person$inf_time <- 0
  person$source <- 0
  person$rec_time <- rexp(1, gamma) # Recovery time
  
  I[[1]] <- person
  all_people[[as.character(person$id)]] <- person
  
  # --- Simulation ---
  while (t < tmax && length(I) > 0) {
    nS <- length(S)
    nI <- length(I)
    
    rate_inf <- beta * nS * nI
    rate_turnover <- delta * (nS + nI)
    
    total_rate <- rate_inf + rate_turnover
    if (total_rate <= 0) break
    
    dt <- rexp(1, total_rate)
    if (t + dt > tmax) break
    t <- t + dt
    
    event <- sample(c("infection", "turnover"), 1, prob = c(rate_inf, rate_turnover))
    
    if (event == "infection" && nS > 0) {
      # Choose active source (recovery time must be in future)
      active_I <- which(sapply(I, function(p) p$rec_time > (t - 1e-9)))
      if (length(active_I) > 0) {
        src_idx <- if(length(active_I) > 1) sample(active_I, 1) else active_I
        rec_idx <- sample(seq_along(S), 1)
        
        source <- I[[src_idx]]
        recipient <- S[[rec_idx]]
        
        recipient$inf_time <- t
        recipient$source <- source$id
        # Ensure rec_time is strictly > inf_time
        recipient$rec_time <- t + rexp(1, gamma)
        
        I[[length(I)+1]] <- recipient
        all_people[[as.character(recipient$id)]] <- recipient
        S <- S[-rec_idx]
      }
    }
    
    if (event == "turnover") {
      total_pop <- nS + nI
      if (runif(1) < nI / total_pop && nI > 0) {
        idx <- sample(seq_along(I), 1)
        I <- I[-idx]
      } else if (nS > 0) {
        idx <- sample(seq_along(S), 1)
        S <- S[-idx]
      }
      
      new_person <- list(id = next_id, inf_time = NULL, rec_time = NULL, source = NULL)
      S[[length(S)+1]] <- new_person
      all_people[[as.character(next_id)]] <- new_person
      next_id <- next_id + 1
    }
    
    # Clean up recovered from the active infectious list
    I <- I[sapply(I, function(p) p$rec_time > t)]
  }
  
  # --- Build output: ONLY include those who were infected ---
  infected_list <- Filter(function(p) !is.null(p$inf_time), all_people)
  
  df <- do.call(rbind, lapply(infected_list, function(p) {
    data.frame(
      inf.ID = p$id,
      inf.times = p$inf_time,
      rec.times = p$rec_time,
      inf.source = p$source
    )
  }))
  
  if (is.null(df)) return(NULL)
  
  df <- df[order(df$inf.times), ]
  return(df)
}
out <- simulate_SIR(N = 50) %>% as.data.frame()

head(out)


```

```{r}
out = simfixoutbreak(out$inf.ID,out$inf.times, out$rec.times, out$inf.source, mut.rate=0.000001, equi.pop=10000, shape=flat,
           inoc.size=1, imp.var=25, samples.per.time=1, samp.schedule="random", 
           samp.freq=500, full=FALSE, feedback=500, glen=100000)

```